Convex Surrogates via Polyhedral Losses

### 2019-04-06 jessie-writeup/jessie-notes.tex
Added section on the mode

\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\path[fill=black, opacity=0.3] (0, 1) --  (0,0) -- (1,0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\fill (-1,0) circle[radius=2pt];
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\fill (0,-1) circle[radius=2pt];
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using Raf's construction.  The given $V$ doesn't yield these subgradients, but there may be another $V$ such that this is also described by the $B_1$ matrix.  We just haven't found it yet.}
\label{fig:abstain-T-report-r1-raf}
\end{figure}

\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\path[fill=black, opacity=0.3] (0, 1) --  (-1/2,1/2) -- (1/2, -1/2) -- (1,0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (-1/2, -1/2) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1/2, -1/2) ;
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_2$ matrix.}
\label{fig:abstain-T-report-r1-B2}
\end{figure}

@@

The polytopes then appear as in Figure~\ref{fig:ranking-polytopes} (and are similar for each cell.)
The large triangle that the polytopes are all inside is $V^\circ$.
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./ranking}
\caption{Polytopes $T(*, y)$ for each $y \in \Y$.}
\label{fig:ranking-polytopes}
\end{figure}

@@

>>>>

\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\path[fill=red, opacity=0.3] (0, 1) --  (0,0) -- (1,0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\fill (-1,0) circle[radius=2pt];
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\fill (0,-1) circle[radius=2pt];
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using Raf's construction.  The given $V$ doesn't yield these subgradients, but there may be another $V$ such that this is also described by the $B_1$ matrix.  We just haven't found it yet.}
\label{fig:abstain-T-report-r1-raf}
\end{figure}

\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\path[fill=red, opacity=0.3] (0, 1) --  (-1/2,1/2) -- (1/2, -1/2) -- (1,0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (-1/2, -1/2) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1/2, -1/2) ;
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_2$ matrix.}
\label{fig:abstain-T-report-r1-B2}
\end{figure}

@@

The polytopes then appear as in Figure~\ref{fig:ranking-polytopes} (and are similar for each cell.)
The large triangle that the polytopes are all inside is $V^\circ$.
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./ranking}
\caption{Polytopes $T(\cdot, y)$ for each $y \in \Y$.}
\label{fig:ranking-polytopes}
\end{figure}

@@

\newpage
\section*{The mode (without nonnegativity constraints)}
Consider a cell for the mode
\[
B = \begin{bmatrix*}
1 & -1 & 0 \\
1 & 0 & -1 
\end{bmatrix*}
\]

We want to see if lifting these nonnegativity constraints leads to (a.) a construction where $0 \in T(r_1, p) \iff p_1 \geq p_2$ and $p_1 \geq p_3$.
(Note that here, we are not requiring $p \in \simplex$.)

Choosing our normals to be
\[
V = \begin{bmatrix*}
1 & 0 \\
0 & 1 
\end{bmatrix*}
\]
We then observe $T(r_1, \cdot)$ as in Figure~\ref{fig:mode-polytopes}.

\begin{figure}
\begin{center}
\begin{minipage}{0.32\linewidth}
\begin{tikzpicture}[scale=1]
\draw[->] (0,0) -- (0,-2);
\draw[->] (0,0) -- (0,2);
\draw[->] (0,0) -- (-2,0);
\draw[->] (0,0) -- (2,0);
\path[fill=red, opacity=0.3] (1, 1) --  (-2,1) -- (-2, -2) -- (1,-2) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.32\linewidth}
\begin{tikzpicture}[scale=1]
\draw[->] (0,0) -- (0,-2);
\draw[->] (0,0) -- (0,2);
\draw[->] (0,0) -- (-2,0);
\draw[->] (0,0) -- (2,0);
\path[fill=black, opacity=0.3] (0, -1) --  (-2,-1) -- (-2, -2) -- (0,-2) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.32\linewidth}
\begin{tikzpicture}[scale=1]
\draw[->] (0,0) -- (0,-2);
\draw[->] (0,0) -- (0,2);
\draw[->] (0,0) -- (-2,0);
\draw[->] (0,0) -- (2,0);
\path[fill=black, opacity=0.3] (-1, 0) --  (-2,0) -- (-2, -2) -- (-1,-2) ;
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ given by the minimal $B$ describing a cell of the mode.}
\label{fig:mode-polytopes}
\end{center}
\end{figure}

Here, we know that $\vec 0 \in T(r_1, p) \iff p_1 = \argmax_i p_i$.
